---
title: "Thou: Romeo's Favorite Word"
description: |
  A text analysis of William Shakespeare's Romeo and Juliet.
author:
  - name: Jennifer Truong
    url: {}
date: 02-25-2021
output:
  distill::distill_article:
    self_contained: false
    code_folding: hide
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(tidytext)
library(textdata)
library(pdftools)
library(ggwordcloud)
library(here)
library(ggpubr)
```

# Read in PDF 

**Text:** *Romeo and Juliet* by William Shakespeare

**Data Source:** Shakespeare, William. “Romeo and Juliet, a Tragedy in Five Acts.” *Internet Archive*, [New York], 1 Jan. 1884, archive.org/details/romeojuliettrage00shak. 

```{r, cache = TRUE}
romeo_juliet_text <- pdf_text("romeo_and_juliet.pdf")
```

# Tidy up PDF
```{r}
romeo_juliet_tidy <- data.frame(romeo_juliet_text) %>% 
  mutate(text_full = str_split(romeo_juliet_text, pattern = "\\r\n")) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_trim(text_full))
```

# Data Wrangling

## Save as Data Frame
```{r}
romeo_juliet_df <- romeo_juliet_tidy %>% 
  slice(-(1:166)) %>% 
  mutate(header = case_when(
    str_detect(text_full, pattern = "ACT") ~ text_full, # Create column for ACT
    TRUE ~ NA_character_
    )) %>% 
  fill(header) %>%
  mutate(header_2 = case_when(
    str_detect(header, pattern = "SCENE") ~ header, # Create column for SCENE
    TRUE ~ NA_character_
    )) %>% 
  #fill(act) #%>% 
  separate(col = header, into = c("act", "act_no"), sep = "     ") #%>% 
  #mutate(chapter_no = as.numeric(as.roman(no)))
```

## Turn everything into tokens and find word count
```{r}
rj_tokens <- romeo_juliet_df%>% 
  unnest_tokens(word, text_full) %>% 
  dplyr::select(-romeo_juliet_text)

# Maybe sort by act and/or scene later when I find out how to tidy those
rj_wordcount <- rj_tokens %>% 
  count(word)
```

## Remove all stop_words that exist in hobbit_tokens

```{r}
rj_nonstop_words <- rj_tokens %>% 
  anti_join(stop_words)

nonstop_counts <- rj_nonstop_words %>% 
  count(word)
```

# Graphs

## Word Cloud! 

```{r}
# Find top 100 words in the play
rj_top100 <- nonstop_counts %>% 
  arrange(-n) %>% 
  slice(1:100)

# Wordcloud time!
rj_cloud <- ggplot(data = rj_top100,
                    aes(label = word)) +
  geom_text_wordcloud(aes(color = n, size = n)) +
  scale_size_area(max_size = 9) +
  scale_color_gradient(low = "sienna1", high = "red3") +
  theme(
    plot.background = element_rect(fill = "gray27"),
    panel.background = element_rect(fill = "black"),
  )

rj_cloud
```

**Figure 1.** The five words with the most occurences throughout the play. 

## Sentiment analysis

Now we'll use the NRC lexicon here!

**Data source:** Saif Mohammad and Peter Turney. (2013), “Crowdsourcing a Word-Emotion Association Lexicon.” Computational Intelligence, 29(3): 436-465.

```{r}
rj_nrc <- rj_nonstop_words %>% 
  inner_join(get_sentiments("nrc"))

rj_nrc_counts <- rj_nrc %>% 
  count(sentiment)

ggplot(data = rj_nrc_counts, 
       aes(x = fct_reorder(sentiment, n), y = n)) +
  geom_col(fill = "red4") +
  labs(x = "Sentiment",
       y = "Number of Occurences",
       title = "NRC Lexicon in Romeo and Juliet") +
  scale_y_continuous(expand = c(0,0)) +
  coord_flip() + 
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid = element_line(color = "rosybrown4",
                              linetype = "dotted"),
    panel.background = element_rect(fill = "navajowhite",
                                    color = "rosybrown4")
  )
```

**Figure 2.** The ranking of sentiment categories from the NRC Lexicon found within *Romeo and Juliet* in descending order.